GRHL2

### 2018-01-25 ChIP-seq_GRHL2/Manuscript_Figures.Rmd
Added Groseq data

---
#Gviz for chr2:11,517,385-11,630,055 #GREB1 and chr17:40,296,682-40,349,154 #RARA
---

>>>>

### GRHL2 overlap with Gro-SEQ data

```{r GroSeq, fig.cap="Gro-Seq data at GRHL2 sites. Blue is control samples, pink is E2 treated samples. Data from GSE43836."}
allPeaks<-read.csv("txt/All_GRHL2_peaks_GSE43836.csv")
upPeaks<-read.csv("txt/Up_GRHL2_peaks_GSE43836.csv")

par(mfrow=c(1,2))

plot(allPeaks[1:2],ylim=c(0,6),type="n", lwd=2, ylab="Read Depth", main="All GRHL2 Sites")
lines(allPeaks[c(1,2)], lwd=2, col="lightblue")
lines(allPeaks[c(1,3)], lwd=2,  col="lightblue")
lines(allPeaks[c(1,4)], lwd=2,  col="pink")
lines(allPeaks[c(1,5)],  lwd=2, col="pink")

plot(upPeaks[c(1,5)],ylim=c(0,6),type="n", ylab="Read Depth", main="E2 responsive GRHL2 Sites")
lines(upPeaks[c(1,2)], lwd=2,col="lightblue")
lines(upPeaks[c(1,3)], lwd=2, col="lightblue")
lines(upPeaks[c(1,4)], lwd=2, col="pink")
lines(upPeaks[c(1,5)],  lwd=2,col="pink")
